Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-12-12 paper.tex
Add refund flow chart

\subsubsection{Refunding}
It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee. To protect consumer rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel. If the expected data is not available, consumers can request refunds. We assume that a very small percentage of consumers in the product contract are irrational and/or malicious. Each consumer can vote for a refund at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transferred to the data provider, broker and every consumer. The subscription fee can be prorated as below:

>>>>

\subsubsection{Refunding}

It is probable that the streaming data sources are delayed or even interrupted after the consumers pay the subscription fee. To protect consumer rights, the subscription fee are not transferred to the data provider until data is generated and published to the MAM channel. If the expected data is not available, consumers can request refunds. We assume that a very small percentage of consumers in the product contract are irrational and/or malicious. Each consumer can vote for a refund at any time. If the ratio of consent votes of refunding is higher than the $threshold$ at the $i$th piece of data, the subscription fee is proportionally transferred to the data provider, broker and every consumer. Figure \ref{fig:refund} shows the refund process.

\begin{figure}[h]
	\centering
	\includegraphics[width=2 in]{refund}
	\caption{The process of the refunding.}
	\label{fig:refund}
\end{figure}

The subscription fee can be prorated as below:
